---
title: "Binomial distributions"
output: html_notebook
---

<h2>Generating distribution samples and calculating probabilities</h2>
<br/> Generate 10 separate random flips with probability 30%:
```{r}
rbinom(10, 1, .3)
```

<br/> Generate 100 occurrences of flipping 10 coins, each with 30% probability:
```{r}
rbinom(100, 10, .3)
```

<br/> Calculate the probability that 2 are heads using dbinom:
```{r}
dbinom(2, 10, .3)
```

<br/> Confirm your answer with a simulation using rbinom:
```{r}
mean(rbinom(10000, 10, .3)==2)
```

<br/> Calculate the probability that at least five coins are heads:
```{r}
1-pbinom(4, 10, .3)
```

<br/> Confirm your answer with a simulation of 10,000 trials:
```{r}
mean(rbinom(10000, 10, .3) >= 5)
```

<h2>Calculating expected value and variance of a binomial distribution</h2>
*Expected value = size \* p* <br/>
*Variance = size \* p \* (1 - p)*

Calculate the expected value of a binomial distribution where 25 coins are flipped, each having a 30% chance of heads using the exact formula:
```{r}
eval_exact <- 25 * .3
eval_exact
```

<br/> Confirm with a simulation using rbinom:
```{r}
mean(rbinom(10000,25,.3))
```

<br/> Calculate the variance using the exact formula:
```{r}
var_exact <- 25 * .3 * (1 - .3)
var_exact
```

<br/> Confirm with a simulation using rbinom
```{r}
var(rbinom(10000,25,.3))
```
